Recursive Neural Network Part-of-Speech Tagger

### 2013-12-20 paper/paper.tex
Fix typo.

The distributed word representations are induced by training a neural network in an unsupervised manner to distinguish a word within its concrete contexts from randomly chosen replacement words within those same contexts, and then back propagating the errors into an $n\times\left\vert\mathcal{V}\right\vert$-dimensional lookup table with randomly initialized values. The lookup table converts between the original ``one-hot" vector representation, which encodes zero information about the word aside from identity, and the superior distributed representation, which encodes a word's contextual information. Since we believe a word's context encodes information about that word's part-of-speech, we hypothesize that distributed word representations will be vital to our part-of-speech tagging model.

>>>>

The distributed word representations are induced by training a neural network in an unsupervised manner to distinguish a word within its concrete contexts from randomly chosen replacement words within those same contexts, and then backpropagating the errors into an $n\times\left\vert\mathcal{V}\right\vert$-dimensional lookup table with randomly initialized values. The lookup table converts between the original ``one-hot" vector representation, which encodes zero information about the word aside from identity, and the superior distributed representation, which encodes a word's contextual information. Since we believe a word's context encodes information about that word's part-of-speech, we hypothesize that distributed word representations will be vital to our part-of-speech tagging model.
